Stability concerns in random matrices

### 2018-03-18 random_matrix_stability.Rmd
Tweak the method for getting data and graphs

>>>>

<!---

Switch code so that the same matrix is checked for stability before and after generation change is added. Then record number stabilised versus unstabilised. Show a plot with the proportion stabilised by varying generation time.

```{r, echo = TRUE, eval = FALSE}
tot_res <- NULL;
res     <- NULL;
for(i in 2:8){
    nn             <- i;
    A1_stt         <- 0;
    A2_stt         <- 0;
    iter           <- 1000000;
    tot_res[[i-1]] <- matrix(data = 0, nrow = iter, ncol = 2);
    while(iter > 0){
        A1_dat  <- runif(n = nn * nn, min = -4, max = 4);
        A1      <- matrix(data = A1_dat, nrow = nn, ncol = nn);
        epsil   <- runif(n = nn, min = 1, max = 1000);
        eps_dat <- rep(x = epsil, times = nn);
        eps_mat <- matrix(data = epsil, nrow = nn, ncol = nn, byrow = FALSE);
        A2      <- A1 * eps_mat;
        A1_stb  <- max(Re(eigen(A1)$values)) < 0;
        A2_stb  <- max(Re(eigen(A2)$values)) < 0;
        if(A1_stb == TRUE){
          A1_stt                  <- A1_stt + 1;
          tot_res[[i-1]][iter, 1] <- 1;
        }
        if(A2_stb == TRUE){
          A2_stt                  <- A2_stt + 1;
          tot_res[[i-1]][iter, 2] <- 1;
        }
        iter    <- iter - 1;
    }
    res <- rbind(res, c(A1_stt, A2_stt));
    print(i);
}
```
--->
